\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-03-13 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added more details about SIMULATION_TYPE == 2

This new release of the code (version 2.1) includes support for GPU graphics card acceleration \citep{KoMiEr09,KoGoErMi10,KoErGoMi10,MiKo10,Kom11}.\\

@@

\item [Numerical simulations in general] ~\\
Forward and adjoint simulations are described in detail in \cite{TrKoLi08,PeKoLuMaLeCaLeMaLiBlNiBaTr11,VaCaSaKoVi99,KoMiEr09,KoErGoMi10,KoGoErMi10,ChKoViCaVaFe07,MaKoDi09,KoViCh10,CaKoLaTiMiLeSnTr08,TrKoHjLiZhPeBoMcFrTrHu10,KoRiTr02,KoTr02a,KoTr02b,KoTr99} or \cite{KoVi98}.
Additional aspects of adjoint simulations are described in
\cite{TrTaLi05,LiTr06,TrKoLi08,LiTr08,TrKoHjLiZhPeBoMcFrTrHu10,PeKoLuMaLeCaLeMaLiBlNiBaTr11}.
Domain decomposition is explained in detail in \cite{MaKoBlLe08}, and excellent scaling up to 150,000 processor cores is shown for instance in
\cite{CaKoLaTiMiLeSnTr08,KoLaMi08a,MaKoBlLe08,KoErGoMi10,KoGoErMi10,Kom11},

\item [GPU computing] ~\\
Computing on GPU graphics cards for acoustic or seismic wave propagation applications
is described in detail in \cite{KoMiEr09,KoGoErMi10,KoErGoMi10,MiKo10,Kom11}.

@@

\noindent
If you use this new version 2.1, which has non blocking MPI for much better performance for medium or large runs, please cite at least one of these six articles,
in which results of non blocking MPI runs are presented: \cite{PeKoLuMaLeCaLeMaLiBlNiBaTr11,KoGoErMi10,KoErGoMi10,KoViCh10,Kom11,CaKoLaTiMiLeSnTr08,MaKoBlLe08}.\\

@@

\caption{Example of a mesh partitioning onto four cores. Each single core partition is colored differently. The executable \texttt{xdecompose\_mesh} can equally distribute the mesh on any arbitrary number of cores.
Domain decomposition is explained in detail in \cite{MaKoBlLe08}, and excellent scaling up to 150,000 processor cores in shown for instance in
\cite{CaKoLaTiMiLeSnTr08,KoLaMi08a,MaKoBlLe08,KoErGoMi10,KoGoErMi10,Kom11}.}

@@

Adjoint simulations are generally performed for two distinct applications.
First, they can be used for earthquake source inversions, especially
earthquakes with large ruptures such as the Lander's earthquake \citep{WaHe94}.
Second, they can be used to generate finite-frequency sensitivity
kernels that are a critical part of tomographic inversions based upon
3D reference models \citep{TrTaLi05,LiTr06,TrKoLi08,LiTr08}. In either
case, source parameter or velocity structure updates are sought to
minimize a specific misfit function (e.g., waveform or traveltime
differences), and the adjoint simulation provides a means of computing
the gradient of the misfit function and further reducing it in successive
iterations. Applications and procedures pertaining to source studies
and finite-frequency kernels are discussed in Sections~\ref{sec:Adjoint-simulation-sources}
and \ref{sec:Adjoint-simulation-finite}, respectively. The two related
parameters in the \texttt{Par\_file} are \texttt{SIMULATION\_TYPE}
(1 or 2) and the \texttt{SAVE\_FORWARD} (boolean).

\section{\label{sec:Adjoint-simulation-sources}Adjoint Simulations for Sources}

>>>>

This new release of the code (version 2.1) includes support for GPU graphics card acceleration \citep{KoMiEr09,KoErGoMi10,MiKo10,Kom11}.\\

@@

\item [Numerical simulations in general] ~\\
Forward and adjoint simulations are described in detail in \cite{TrKoLi08,PeKoLuMaLeCaLeMaLiBlNiBaTr11,VaCaSaKoVi99,KoMiEr09,KoErGoMi10,ChKoViCaVaFe07,MaKoDi09,KoViCh10,CaKoLaTiMiLeSnTr08,TrKoHjLiZhPeBoMcFrTrHu10,KoRiTr02,KoTr02a,KoTr02b,KoTr99} or \cite{KoVi98}.
Additional aspects of adjoint simulations are described in
\cite{TrTaLi05,LiTr06,TrKoLi08,LiTr08,TrKoHjLiZhPeBoMcFrTrHu10,PeKoLuMaLeCaLeMaLiBlNiBaTr11}.
Domain decomposition is explained in detail in \cite{MaKoBlLe08}, and excellent scaling up to 150,000 processor cores is shown for instance in
\cite{CaKoLaTiMiLeSnTr08,KoLaMi08a,MaKoBlLe08,KoErGoMi10,Kom11},

\item [GPU computing] ~\\
Computing on GPU graphics cards for acoustic or seismic wave propagation applications
is described in detail in \cite{KoMiEr09,KoErGoMi10,MiKo10,Kom11}.

@@

\noindent
If you use this new version 2.1, which has non blocking MPI for much better performance for medium or large runs, please cite at least one of these six articles,
in which results of non blocking MPI runs are presented: \cite{PeKoLuMaLeCaLeMaLiBlNiBaTr11,KoErGoMi10,KoViCh10,Kom11,CaKoLaTiMiLeSnTr08,MaKoBlLe08}.\\

@@

\caption{Example of a mesh partitioning onto four cores. Each single core partition is colored differently. The executable \texttt{xdecompose\_mesh} can equally distribute the mesh on any arbitrary number of cores.
Domain decomposition is explained in detail in \cite{MaKoBlLe08}, and excellent scaling up to 150,000 processor cores in shown for instance in
\cite{CaKoLaTiMiLeSnTr08,KoLaMi08a,MaKoBlLe08,KoErGoMi10,Kom11}.}

@@

Adjoint simulations are generally performed for two distinct applications.
First, they can be used for earthquake source inversions, especially
earthquakes with large ruptures such as the Lander's earthquake \citep{WaHe94}.
Second, they can be used to generate finite-frequency sensitivity
kernels that are a critical part of tomographic inversions based upon
3D reference models \citep{TrTaLi05,LiTr06,TrKoLi08,LiTr08}. In either
case, source parameter or velocity structure updates are sought to
minimize a specific misfit function (e.g., waveform or traveltime
differences), and the adjoint simulation provides a means of computing
the gradient of the misfit function and further reducing it in successive
iterations. Applications and procedures pertaining to source studies
and finite-frequency kernels are discussed in Sections~\ref{sec:Adjoint-simulation-sources}
and \ref{sec:Adjoint-simulation-finite}, respectively. The two related
parameters in the \texttt{Par\_file} are \texttt{SIMULATION\_TYPE}
(1, 2 or 3) and the \texttt{SAVE\_FORWARD} (boolean).

\section{\label{sec:Adjoint-simulation-sources}Adjoint Simulations for Sources Only (not for the Model)}
